Ore Polynomials in Sage

### 2013-06-14 paper/main.tex
Added introduction to section 4 of the paper. Changed the way a polynomial remainder sequence is chosen.

@@

A univariate Ore algebra over a field is a left Euclidean domain, which means that it is possible to perform 
left division with remainder. Building upon this, the greatest common right divisor (GCRD) and the least common 
left multiple (LCLM) of two Ore polynomials can be computed. The package provides a number of methods to carry 
out these tasks

\begin{center}
  \begin{tabular}{|l|p{.55\hsize}|}
    \hline
    Method name & short description \\\hline
    \verb|quo_rem(B)| & returns the left quotient and the left remainder of $A$ and $B$.\\
    \verb|gcrd(B)| & returns the greatest common right divisor of $A$ and $B$.\\
    \verb|xgcrd(B)| & returns the greatest common right divisor of $A$ and $B$ and the according B\'ezout coefficients.\\
    \verb|lclm(B)| & returns the least common left multiple of $A$ and $B$.\\\hline
  \end{tabular}
\end{center}

All these methods are also available for Ore operators living in univariate Ore algebras over a base ring $R$ which 
does not necessarily have to be a field. The operators are then implicitly assumed to live in the respective Ore 
algebra over the quotient field $K$ of $R$. The output will be the GCRD (LCLM, quotient, remainder) in the Ore 
algebra over $K$ but not over $R$, in which these objects might not exist or might not be computable.

@@

\begin{sageexample}
  sage: A = OreAlgebra(ZZ['n'], 'Sn');                                           
  sage: L1,L2 = A.random_element(3),A.random_element(2)    
  sage: L1.gcrd(L2, prs=__primitivePRS__)
  sage: L1.gcrd(L2, prs=__classicPRS__)
\end{sageexample}

>>>>

Besides basic arithmetic for Ore operators, the package provides a wide range of methods to create, manipulate and solve several different kinds of functional equations. 
Some of these methods are accessible in any Ore algebra while others are tied specifically to e.g.\ recurrence operators or differential operators.
In these predefined algebras, operators can act on suitable objects like functions or sequences in a natural way:

\begin{sageexample}
  sage: R.<x> = PolynomialRing(QQ)
  sage: A = OreAlgebra(R, 'Dx'); Dx=A.gen() 
  sage: p,q = R.random_element(3),R.random_element(1)
  sage: L = p*Dx - p.derivative()
  sage: L(p)
  sage: L(q)
\end{sageexample}

It is also possible to define actions for other Ore algebras or to redefine the action in the predefined ones.

\begin{sageexample}
  sage: R.<x> = PolynomialRing(QQ)
  sage: A = OreAlgebra(R, ('S', {x:x+1}, {x:1})); S=A.gen()
  sage: B = OreAlgebra(R, 'Dx'); Dx=B.gen()
  sage: S(x-1,action=lambda x: 2*x)
  sage: Dx(x,action=lambda x: x)
  sage: Dx(x)
\end{sageexample}

We give a small overview of the functionality of some selected methods.

@@

A univariate Ore algebra over a field is a left Euclidean domain, which means that it is possible to perform 
left division with remainder. Building upon this, the greatest common right divisor (GCRD) and the least common 
left multiple (LCLM) of two Ore polynomials can be computed. The package provides a number of methods to carry 
out these tasks.

\begin{center}
  \begin{tabular}{|l|p{.55\hsize}|}
    \hline
    Method name & short description \\\hline
    \verb|quo_rem(B)| & returns the left quotient and the left remainder of $A$ and $B$.\\
    \verb|gcrd(B)| & returns the greatest common right divisor of $A$ and $B$.\\
    \verb|xgcrd(B)| & returns the greatest common right divisor of $A$ and $B$ and the according B\'ezout coefficients.\\
    \verb|lclm(B)| & returns the least common left multiple of $A$ and $B$.\\
    \verb|xlclm(B)| & returns the least common left multiple $L$ of $A$ and $B$ and the left quotients of $L$ and $A$ and of $L$ and $B$.\\\hline
  \end{tabular}
\end{center}

All these methods are also available for Ore operators living in univariate Ore algebras over a base ring $\set R$ which 
does not necessarily have to be a field. The operators are then implicitly assumed to live in the respective Ore 
algebra over the quotient field $\set K$ of $\set R$. The output will be the GCRD (LCLM, quotient, remainder) in the Ore 
algebra over $\set K$ but not over $\set R$, in which these objects might not exist or might not be computable.

@@

\begin{sageexample}
  sage: A = OreAlgebra(ZZ['n'], 'Sn');                                           
  sage: L1,L2 = A.random_element(3),A.random_element(2)    
  sage: L1.gcrd(L2, prs="primitive")
  sage: L1.gcrd(L2, prs="monic")
\end{sageexample}
